---
title: Generalized Assignment Problem
---

```{r echo = FALSE}
library(rmarkdown)
library(tidyr)

knitr::opts_chunk$set(
  out.width = "100%"
)

```

```{r}
time_limit = 3600

results = read.csv("../results_GAP_idol.csv", header = FALSE)
colnames(results) = c("instance", "solver", "with_heuristics", "smoothing_factor", "farkas_pricing", "clean_up_threshold", "branching_on_master", "status", "reason", "n_agents", "n_jobs", "objective_value", "time")

results[results$solver == "external_solver",]$with_heuristics = NA
results[results$solver == "external_solver" | results$solver == "idol_bab",]$smoothing_factor = NA
results[results$solver == "external_solver" | results$solver == "idol_bab",]$farkas_pricing = NA
results[results$solver == "external_solver" | results$solver == "idol_bab",]$clean_up_threshold = NA
results[results$solver == "external_solver" | results$solver == "idol_bab",]$branching_on_master = NA

results$solver_with_params = paste0(results$solver, "_h", results$with_heuristics, "_s", results$smoothing_factor * 100, "_f", results$farkas_pricing, "_c", results$clean_up, "_m", results$branching_on_master)
results[results$solver == "external_solver",]$solver_with_params = "external_solver"
results[results$solver == "idol_bab",]$solver_with_params = paste0("idol_bab_h", results[results$solver == "idol_bab",]$with_heuristics)
```

```{r echo = FALSE}
paged_table(results)
```

```{r}
solvers = as.data.frame(unique(results$solver_with_params))
colnames(solvers) = "Solver"
```

```{r echo = FALSE}
knitr::kable(solvers)
```

## Performance profiles

```{r}
performance_profile = function (dataset, color = NULL, xlim = NULL, main = "Performance profile") {
  
  solvers = unique(dataset$solver_with_params)
  times = spread(dataset[,c("instance", "solver_with_params", "time")], key = solver_with_params, value = time)
  times = na.omit(times)
  times$time.best = apply(times[,-1], 1, FUN = min)
  
  ratios = times[,-ncol(times)][,-1] / times$time.best
  colnames(ratios) = paste0(colnames(ratios), ".ratio")
  
  worst_ratio = max(ratios)
  
  times = cbind(times, ratios)
  
  for (solver in solvers) {
    time_limit_filter = times[,solver] >= time_limit
    if ( sum(time_limit_filter) > 0 ) {
      times[time_limit_filter, paste0(solver, ".ratio")] = worst_ratio
    }
  }
  
  if (is.null(xlim)) {
    xlim = c(1, worst_ratio)
  }
  
  if (is.null(color)) {
    color = rainbow(length(solvers))
  }
  
  par(mar = c(5,4,4,8))
  
  index = 1
  for (solver in solvers) {
    
    plot_function = if (index == 1) plot else lines
    
    profile = ecdf(times[,paste0(solver, ".ratio")])
    
    plot_function(profile, xlim = xlim, ylim = c(0,1), lty = "solid", cex = 0, col = color[index], main = "", xlab = "", ylab = "")
    
    index = index + 1
  }
  
  # Set the plot title
  title(main = main,
        xlab = "Performance ratio",
        ylab = "ECDF")
  
  # Set the plot legend
  legend(
    "topright",
    inset=c(-.35, 0),
    legend = solvers,
    lty = "solid",
    col = color,
    cex = .5,
    xpd = TRUE,
    bty = "n"
  )
  
}
```

### Over all methods

#### Really all

Comparing all the solvers.

```{r}
performance_profile(results, xlim = c(1, 200))
```
#### With specified settings

Comparing the external solver with branch-and-bound and branch-and-price with specific settings.

```{r}
performance_profile(results[results$solver_with_params %in% c("external_solver", "idol_bab_h1", "idol_bap_h1_s30_f0_c500_m1"),], xlim = c(1, 200), main = "External solver, BaB and BaP")
```

### Branch and bound

Comparing branch-and-bound with and without heuristics.

```{r}
performance_profile(results[results$solver == "idol_bab",], xlim = c(1, 3), main = "With and without heuristics")
```


### Branch and price

#### Branching on master versus branching on pricing

Comparing branching scheme (on master or on pricing problem) without smoothing, using artificial variables (phase I) and primal heuristics.

```{r}
performance_profile(results[results$solver == "idol_bap" & results$with_heuristics == TRUE & results$smoothing_factor == 0 & results$farkas_pricing == 0,], xlim = c(1, 3), main = "Branching on master versus subproblem")
```

#### Using artificial variables versus Farkas pricing

Comparing farkas pricing with artificial variables (phase I) using primal heuristics, master branching and no smoothing.

```{r}
performance_profile(results[results$solver == "idol_bap" & results$with_heuristics == TRUE & results$smoothing_factor == 0 & results$branching_on_master == TRUE,], xlim = c(1, 3), main = "Using artificial costs versus Farkas pricing")
```

#### Smoothing factor

Comparing smoothing factors with artificial variables, master branching and primal heuristics.

```{r}
performance_profile(results[results$solver == "idol_bap" & results$with_heuristics == TRUE & results$branching_on_master == TRUE & results$farkas_pricing == 0,], xlim = c(1, 3), main = "Smoothing factor")
```